Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings

### 2015-09-25 manuscript/manuscript_pve.Rmd
pixiedust tables into manuscript

@@

# Tables {.unnumbered}
**Table 1**.

\
**Table 2**.
<!---
![table2](harvesttable.jpg)
![table2](phystable.jpg)
![table3](modeltable.jpg)
-->

<!---
```{r table1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
pve_data <- read.csv("master_scripts/pve_table1.csv")

colnames(pve_data) <- c("Volume (L)", 
                        "Seedling~mass~(g)", 
                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
                        "Leaf~Starch~(\\%)", 
                        "Leaf~Sugars~(\\%)", 
                        "Leaf~Nitrogen~(\\%)",
                        "Root~Nitrogen~(\\%)",
                        "SRL~(cm~m\\textsuperscript{-1})",
                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")
print(ascii(pve_data,include.rownames=FALSE),type='pandoc')

```
**Table 1.** Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Seedling mass, SRL, root nitrogen and leaf $\delta$^13C values are from final harvest. Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6). Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
phys_data <- read.csv("master_scripts/pve_table2.csv")
colnames(phys_data) <- c("Volume (L)", 
                        "\\textit{A}\\textsubscript{max}", 
                        "\\textit{R}\\textsubscript{dark}",
                        "\\textit{J}\\textsubscript{max}",
                        "\\textit{Vc}\\textsubscript{max}",
                        "\\textit{g}\\textsubscript{s}",
                        "\\textit{g}\\textsubscript{1}")
print(ascii(phys_data,include.rownames=FALSE),type='pandoc')

```
**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C. Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6). R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements. Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
-->

>>>>

#table data
library(pixiedust)
table1 <- read.csv("master_scripts/pve_table1.csv")
table2 <- read.csv("master_scripts/pve_table2.csv")

@@

# Tables {.unnumbered}
**Table 1**.Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Seedling mass, SRL, root nitrogen and leaf $\delta$^13^C values are from final harvest. Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6). Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.

```{r, echo=FALSE, warning=FALSE}
greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')

dust(table1)+
  sprinkle_colnames("Volume (L)", 
                        "Seedling~mass (g)", 
                        "SLA TNC-free (m^2^ kg^-1^)",
                        "Leaf Starch (%)", 
                        "Leaf Sugars (%)", 
                        "Leaf Nitrogen (%)",
                        "Root Nitrogen (%)",
                        "SRL (cm m^-1^)",
                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) +
  sprinkle(rows= 1, part="head",bold=TRUE)+
  sprinkle_print_method("markdown")
```

\
**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C. Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6). R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements. Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.

```{r table2, echo=FALSE, warning=FALSE}
dust(table2)+
  sprinkle_colnames("Volume (L)", 
                        "A~max~", 
                        "R~dark~",
                        "J~max~",
                        "Vc~max~",
                        "g~s~",
                        "g~1~") +
  sprinkle(rows= 1, part="head",bold=TRUE)+
  sprinkle_print_method("markdown")
```
